### 2023-12-28 doc/Thesis/chapter/021-theory-calculations.tex
rename to fit numbering

(2) If the query space is so vast, that randomly querying might explore domains which might lead to uninteresting or even misleading information.
%Both encompass nearly all cases. 
% 
At the beginning of any experiment its constraints must be determined. 
%
Constraints for a given experiment include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
%

%FULL FACTORIAL
A naive approach to an experiment design is the full factorial \gls{doe}.
Each possible combination of discrete values is tested. 
While this is the most informative design it will more often than not be infeasible due the curse of dimensionality\cite{cherkassky1998learning}.
% 2-LVL FACTORIAL
The 2-level factorial design provides an alternative with $2^d$ experiments (where $d$ is the number of independent variables). 
Drawbacks of 2-level factorial \gls{doe}s include no data about the inside of the search space and infeasibility for high dimensional problems.
In a full factorial or 2-level factorial design most experiments are redundant and most resources will be spent exploring high-order interaction effects\cite{gunst2009fractional}, which are often minimal to non-existent.
% RANDOM 
In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
When a subset is chosen from the factorial design, it is called a fractional factorial design. 
% PLACKETT_BURMAN
The \gls{pb}\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
where the number of needed experiments $n$ is $n<d+4$ 
(more precisely $n=(\lfloor d\div4\rfloor+1)\cdot4$, where $\lfloor x\rfloor$ denotes the floor function on $x$).
The \gls{pb} design ensures that each combination of levels for any pair of factors appears the same number of times. 
% HAMMERSLEY 
A drawback of 2-level factorial (incl. \gls{pb}) and random fractional designs is that the sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
% LATIN HYPER CUBE
The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
which has the feature that each level for each variable will be tested only once. 
A Latin hypercube \gls{doe} can be also created such that data points distribute more uniformly over the search space. 
Latin hypercube \gls{doe}s are mainly used in computer simulations which are purely deterministic and therefore are very precise.
%
%Continuous state spaces must be accommodated by arbitrary discretization.
%\cite{cohn1996neural}
\iffalse
%
\td{For any 2-level factorial DOE applies: "The effect of any factor main effect (A, B, C) or interaction (AB, AC, BC, ABC) is the difference of two averages, the average of the responses correpsonding to +1 levels and the average of the responses corresponding to -1 levels. " - from Gunst2009\cite{gunst2009fractional}}

>>>>

(2) If the query space is so vast, that randomly querying might explore domains\td{, which} might lead to uninteresting or even misleading information.
%Both encompass nearly all cases. 
% 
At the beginning of any experiment its constraints must be determined. 
%
Constraints for a given experiment include range of input and output variables as well as total time available and total number of samples/experiments that can be taken\cite{goodwin1977experiment}.

%FULL FACTORIAL
A naive approach to an experiment design is the full factorial \gls{doe}.
Each possible combination of discrete values is tested.
\td{While} this is the most informative design it will more often than not be infeasible due the curse of dimensionality\cite{cherkassky1998learning}.
% 2-LVL FACTORIAL
The 2-level factorial design provides an alternative with $2^d$ experiments (where $d$ is the number of independent variables). 
Drawbacks of 2-level factorial \gls{doe}s include no data about the inside of the search space and infeasibility for high dimensional problems.
In a full factorial or 2-level factorial design most experiments are redundant and most resources will be spent exploring high-order interaction effects\cite{gunst2009fractional}, which are often minimal to non-existent.
% RANDOM 
In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
When a subset is chosen from the factorial design, it is called a fractional factorial design. 
% PLACKETT_BURMAN
The \gls{pb}\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of 2-level fractional factorial design, 
where the number of needed experiments $n$ is $n<d+4$ 
(more precisely $n=(\lfloor d\div4\rfloor+1)\cdot4$, where $\lfloor x\rfloor$ denotes the floor function on $x$).
The \gls{pb} design ensures that each combination of levels for any pair of factors appears the same number of times. 
% HAMMERSLEY 
A drawback of 2-level factorial (incl. \gls{pb}) and random fractional designs is that the sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
% LATIN HYPER CUBE
The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
which has the feature that each level for each variable will be tested only once. 
A Latin hypercube \gls{doe} can be also created such that data points distribute more uniformly over the search space. 
Latin hypercube \gls{doe}s are mainly used in computer simulations which are purely deterministic and therefore are very precise.
%
%Continuous state spaces must be accommodated by arbitrary discretization.
%\cite{cohn1996neural}
\iffalse
%
\td{For any 2-level factorial DOE applies: "The effect of any factor main effect (A, B, C) or interaction (AB, AC, BC, ABC) is the difference of two averages, the average of the responses correpsonding to +1 levels and the average of the responses corresponding to -1 levels. " - from Gunst2009\cite{gunst2009fractional}}

### 2023-12-28 doc/Thesis/chapter/023-linreg-krr-svm.tex
rename to fit numbering

\textbf{Ridge Regression} is like linear regression with an extra term which penalizes steep regression functions.
The extra term reduces overfitting and is scaled by a correction parameter~$\alpha$. 
The larger $\alpha$ is, the larger is the regularization and the flatter is the regression functions. 
When $\alpha$ tends to infinity, we get an intercept-only model.
When $\alpha$ is zero, the regularized loss function becomes the $L_2$ loss function.
%\td{A critique of ridge regression is that all the variables tend to end up in the model. The model only shrinks the coefficients.}
\begin{equation}
    L_{RR} = L_2 + \alpha \sum |k_i| = \sum(y_i - \hat y_i)^2 + \alpha \sum |k_i| 
\end{equation}

@@

which can be rewritten by some mathematical wizardry (setting the partial derivatives of the Lagrangian function

@@

If the prediction $(\mathbf{w}\mathbf{x}_i+b)$ and the true category $y_i$ don't agree, 

@@

Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the innerproduct of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper. 
%\td{write about sv regrgession}

>>>>

\textbf{Ridge Regression} is like linear regression with an extra term which penalizes steep regression functions.
The extra term reduces overfitting and is scaled by a correction parameter~$\alpha$. 
The larger $\alpha$ is, the larger is the regularization and the flatter is the regression function. 
When $\alpha$ tends to infinity, we get an intercept-only model.
When $\alpha$ is zero, the regularized loss function becomes the $L_2$ loss function.
%\td{A critique of ridge regression is that all the variables tend to end up in the model. The model only shrinks the coefficients.}
\begin{equation}
    L_{RR} = L_2 + \alpha \sum |k_i| = \sum(y_i - \hat y_i)^2 + \alpha \sum |k_i| 
\end{equation}

@@

which can be rewritten by some \td{mathematical wizardry} (setting the partial derivatives of the Lagrangian function

@@

If the prediction $(\mathbf{w}\mathbf{x}_i+b)$ and the true category $y_i$ do not agree, 

@@

Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the innerproduct of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper. 
%\td{write about sv regrgession}

### 2023-12-28 doc/Thesis/chapter/04-computational-details.tex
rename to fit numbering

\section{Data Processing}
\label{sec:eval}
%Reading list
%\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
%    \item 
%\end{itemize}
%\td{describe problem and solution found}
Multiple \gls{iv} curves were measured for every sample.
The main difficulty faced in processing the data was to present the measurements obtained 
from a sample in one representative number. 
%
%\todo{why didn't i just take this?}
%\td{L2 norm because it might be easier to compare to other methods. }
%\td{inspired by euclidean norm/L2 distance from ideal case} 
%\td{wanted to put more weight on bad shunts}
%\td{plot avg, avg(log), avg(log-13)}
%
For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
5 points before and 5 points after the origin with minimum one point distance from zero (which boils
down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
calculating averages $\overline{V}$ and $\overline{I}$ of each point cloud and taking the ratio of differences:
%averaging their V and I values and calculating
\begin{equation}
    %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}
\end{equation}
%
The average of each conductance would be an easy and naive choice but difficult to represent a 
sample correctly since the possible values of conductance span across several magnitudes.
So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
%
In order to make the metric closer 
%and better comparable to the 
\gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 
%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
%and the mean of all conductances was taken
%
\begin{equation}
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	\label{eq:gamma}
\end{equation}
Another measure is the density of shorted species $\rho$ (pin hole density), calculated in following way:
\begin{equation}
	s_i = \begin{cases}
        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho = \sum_i^N \frac{s_i}{N}
	\label{eq:rho}
\end{equation}
The density is 1 if every measurement has a conductance larger than $10^{-5} \, \Omega^{-1}$ and is 0 if every measured conductance has a value of smaller than $10^{-5} \, \Omega^{-1}$.
%Other estimates of the conductance are the averages:
%\begin{equation}
%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
%\end{equation}
%
%\begin{equation}
%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
%%\end{equation}

\section{Sample Selection}
\label{sec:ss}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$\lambda$	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $\lambda$ and $v_{cal}$, 
where $\gamma$, $\rho$ and $\lambda$ are to be minimized and $v_{cal}$ to be maximized.
%which all should be minimized except for $v_{cal}$.
The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The experiments are executed, measured and evaluated according to section 
\ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pin hole density $\rho_s$ (see eq. \ref{eq:rho}), 
$\lambda$ (numbers of layers) and $v_{cal}$ (heating rate of calcination process in 
\oc{}/\minutes{}) are supplied to the program. 
The program, then, uses this data to estimate a response for each output variable 
for the entire population space
(and to choose a fraction of the initial population which is allowed to propagate).
%The response variables for the entire population space is calculated. 
The current population - each of the particles independently - 
are given a random velocity vector associated to them which is directed to the best predicted sample. 
%moves towards the optimum solution.
The population for the next time step is generated and the experiments are again executed, measured and evaluated.
Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.

@@

\section{Fitting via Machine Learning}
%\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with polynomial, \gls{rbf} and sigmoid kernels. 
%\subsection{Grid Search}
A grid search over a set of hyperparameters was executed. 
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
% KRR 
The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5 and 10.
%and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
% SVM
The kernels for \gls{svm} were the same as for \gls{krr}. 
Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$. 
$C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05 for \gls{svm} and \gls{krr}.
\Gls{svm} additionally used the \texttt{scale} for $\gamma_{ml}$.
%\td{and was the same as for \gls{krr} plus \texttt{scale}.} %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
\texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
% GRID SEARCH 
The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
of the \gls{emma} data set were scaled with the routine \texttt{sklearn.preprocessing.StandardScaler().fit\_transform()}. %\td{scaled before each calculation.}
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
% https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVR.html#sklearn.svm.SVR.score
For each calculation the 5-fold cross validation score was calculated. 
The score equals to the coefficient of determination $R^2$ which is defined the following for non-linear regression functions
%\footnote{see https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html\#sklearn.kernel\_ridge.KernelRidge.score}
\footnote{see \href{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}}
\begin{equation}
	\label{eq:r2}
	R^2 = 1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}
\end{equation}
For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 
the parameters with the highest score were noted.
% 
Finally, the different data sets were predicted for each model and \gls{mae} and \gls{mse} were calculated.
These values were also calculated for \gls{emma} and the linear model in order to compare the different methods.

>>>>

\todo{ To me this does not follow any logical order!}
\section{Data Processing}
\label{sec:eval}
\todo{Why this procedure? Sounds quite arbitrary?}
%Reading list
%\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
%    \item 
%\end{itemize}
%\td{describe problem and solution found}
\td{Multiple \gls{iv} curves were measured (where are they?)} for every sample.
The main difficulty faced in processing the data was to present the measurements obtained 
from a sample in one representative number. 
%
%\todo{why didn't i just take this?}
%\td{L2 norm because it might be easier to compare to other methods. }
%\td{inspired by euclidean norm/L2 distance from ideal case} 
%\td{wanted to put more weight on bad shunts}
%\td{plot avg, avg(log), avg(log-13)}
%
For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
5 points before and 5 points after the origin with minimum one point distance from zero (which boils
down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
calculating averages $\overline{V}$ and $\overline{I}$ of each point cloud and taking the ratio of differences:
%averaging their V and I values and calculating
\begin{equation}
    %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}
\end{equation}
%
The average of each conductance would be an easy and naive choice but difficult to represent a 
sample correctly since the possible values of conductance span across several magnitudes.
So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
%
In order to make the metric closer 
%and better comparable to the 
\gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 
%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
%and the mean of all conductances was taken
%
\begin{equation}
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	\label{eq:gamma}
\end{equation}
Another measure is the density of shorted species $\rho$ (pinhole density), calculated in following way:
\begin{equation}
	s_i = \begin{cases}
        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho = \sum_i^N \frac{s_i}{N}
	\label{eq:rho}
\end{equation}
The density is 1 if every measurement has a conductance larger than $10^{-5} \, \Omega^{-1}$ and is 0 if every measured conductance has a value of smaller than $10^{-5} \, \Omega^{-1}$.
%Other estimates of the conductance are the averages:
%\begin{equation}
%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
%\end{equation}
%
%\begin{equation}
%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
%%\end{equation}

\section{Sample Selection}
\label{sec:ss}
\todo{for what?}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$\lambda$	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be \td{$\gamma$, $\rho$, $\lambda$ and $v_{cal}$, (here it would help me to remind the reader what the symbols are!)}
where $\gamma$, $\rho$ and $\lambda$ are to be minimized and $v_{cal}$ to be maximized.
%which all should be minimized except for $v_{cal}$.
The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The \td{experiments} are executed, \td{measured (unclear!)} and evaluated according to section 
\ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), 
\todo{$\lambda$ (numbers of layers) (tstill not clear! what is meant?!)} and $v_{cal}$ (heating rate of calcination process in 
\oc{}/\minutes{}) are supplied to the program. 
The program, then, uses this data to estimate a response for each output variable 
for the entire population space
(and to choose a fraction of the initial population which is allowed to propagate).
%The response variables for the entire population space is calculated. 
The current population - each of the particles independently - 
are given a random velocity vector associated to them, which is directed to the best predicted sample. 
%moves towards the optimum solution.
The population for the next time step is generated and the experiments are again \td{executed, measured and evaluated. (unclear!)}
Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.

@@

\section{Fitting via Machine Learning}
%\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with polynomial, \gls{rbf} and sigmoid kernels. 
%\subsection{Grid Search}

A grid search over a set of hyperparameters was executed. 
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
% KRR 
The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5 and 10.
%and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
% SVM
The kernels for \gls{svm} were the same as for \gls{krr}. 
Further hyper parameters were \td{$C$, $\varepsilon$ and $\gamma_{ml}$. 
$C$ and $\varepsilon$ (define again, forgotten until now) } took the values 0.05--1 with step size 0.05 for \gls{svm} and \gls{krr}.
\Gls{svm} additionally used the \texttt{scale} for $\gamma_{ml}$.
%\td{and was the same as for \gls{krr} plus \texttt{scale}.} %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
\texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
% GRID SEARCH 
The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
of the \gls{emma} data set were scaled with the routine \texttt{sklearn.preprocessing.StandardScaler().fit\_transform()}. %\td{scaled before each calculation.}
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
% https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVR.html#sklearn.svm.SVR.score
For each calculation the 5-fold cross-validation score was calculated. 
The score equals to the coefficient of determination $R^2$, which is defined the following for non-linear regression functions:
%\footnote{see https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html\#sklearn.kernel\_ridge.KernelRidge.score}
\footnote{see \href{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}}
\begin{equation}
	\label{eq:r2}
	R^2 = 1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}
\end{equation}
For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 
the parameters with the highest score were noted.

Finally, the different data sets were predicted for each model and \gls{mae} and \gls{mse} were calculated.
These values were also calculated for \gls{emma} and the linear model in order to compare the different methods. 
\todo{(and how did this output help you to optimize your exp. procedure??)}
